---
title: "Tutorial 6: Refactoring R Code"
format: html
---

# Introduction

In this tutorial, you will refactor the code into separate scripts corresponding to each section. The dataset we will use comes from the `palmerpenguins` package, which contains measurements of penguins from three species.

## Load Libraries and Data

```{r}
#| echo: fenced
source("R/01_load_data.R")
data <- load_and_clean_data()
```

# Methods

In this section, we perform exploratory data analysis (EDA) and prepare the data for modeling.

```{r}
#| echo: fenced
source("R/02_eda.R")
data <- perform_eda(data)
```

# Model

We will fit a classification model using `tidymodels` to predict the species of a penguin based on its physical characteristics.

```{r}
#| echo: fenced
source("R/03_train.R")
model_results <- train_model(data)
penguin_fit <- model_results$penguin_fit
test_data <- model_results$test_data
```

# Results

We evaluate the performance of the model using the test dataset.

```{r}
#| echo: fenced
source("R/04_evaluate.R")
conf_mat <- evaluate_model(penguin_fit, test_data)
conf_mat
```

# Conclusion

In this tutorial, we:

- Loaded and cleaned the `palmerpenguins` dataset.
- Performed exploratory data analysis.
- Built a k-Nearest Neighbors classification model using `tidymodels`.
- Evaluated the model's performance.
